Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-04-20 revision-1/model.tex
checkpoint

$$
\begin{array}{rclr}
  (\store, \eassign{\mesg{w}}{\cid_1}{\be}{\cid_2};\prog) &\aredx&
  (\extend{\store}{\mesg{w}_{\cid_1}}{\lcod{\store,\be}{\cid_2}}, \prog) & \cid_2 \in H\\
  (\store, \eassign{\mesg{w}}{\cid_1}{\be}{\cid_2};\prog) &\aredx&
  (\extend{\store}{\mesg{w}_{\cid_1}}{\lcod{\arewrite(\store_C,\be)}{\cid_2}}, \prog) & \cid_2 \in C
\end{array}
$$

$$
\dist(\SIM(\store_{S_H})) = \condd{\progtt(\prog)}{\houtputs \cup O_H}{\store_{S_H}}
$$

>>>>

In the malicious model we assume that corrupt clients are in the thrall of an
adversary $\adversary$ who does not necessarily follow the rules of the protocol.
We model this by positing a $\arewrite$ function which is given a corrupt memory
$\store_C$ and expression $\be$, and returns a rewritten expression that can
be interpreted to yield a corrupt input. Then we define an evaluation
relation that incorporates the adversary:
$$
\begin{array}{rclr}
  (\store, \eassign{\mesg{w}}{\cid_1}{\be}{\cid_2};\prog) &\aredx&
  (\extend{\store}{\mesg{w}_{\cid_1}}{\lcod{\store,\be}{\cid_2}}, \prog) & \cid_2 \in H\\
  (\store, \eassign{\mesg{w}}{\cid_1}{\be}{\cid_2};\prog) &\aredx&
  (\extend{\store}{\mesg{w}_{\cid_1}}{\lcod{\arewrite(\store_C,\be)}{\cid_2}}, \prog) & \cid_2 \in C
\end{array}
$$
Given this we define the $\adversary$ distribution of $\prog$. 
\begin{definition}
  \label{def-progd}
  \label{definition-progd}
  Given program $\prog$ with $\secrets(\prog) = S$ and $\flips(\prog) = R$, and
  any assumed pre-processing predicate $\preproc$ on memories, define:
  $$
  \aruns(\prog) \defeq \{ \store \mid \preproc(\store) \wedge
  (\dom(\store) = \iov(\prog) \cup R) \wedge (\store_{S \cup R},\prog) \aredx^* (\store,\varnothing) \}
  $$
  Then the \emph{$\adversary$ distribution of $\prog$}, written $\progtt(\prog,\adversary)$, is
  defined such that for all $\store \in \mems(\iov(\prog) \cup R)$:
  $$
  \progtt(\store) =  1 / |\runs(\prog)| \ \text{if}\ \store \in \aruns(\prog), \text{otherwise}\ 0
  $$
\end{definition}

\begin{definition}[Malicious Security]
  Let $\prog$ be a protocol with $\iov(\prog) = S \cup V \cup O$. We say that
  $\prog$ is \emph{malicious secure} iff for all
  partitions of the federation into honest and corrupt sets $H$ and $C$,
  adversaries $\adversary$, 
  and all $\store \in \mems(S_H)$ there exists a
  simulation $\SIM$ which is given $\store$ and has two phases:
  \begin{enumerate}
  \item In the first phase (aka input extraction), $\adversary$ gives the
    simulator some $\store' \in \mems(S_C)$, and the simulator consults an
    oracle to compute $\idealf(\store \cup \store')$.
  \item In the second phase, $\SIM$ reconstructs corrupt views $\houtputs$,
    which it returns along with the honest outputs in $\idealf(\store \cup \store')$, such that:
    $$
    \dist(\SIM(\store)) = \condd{\progtt(\prog,\adversary)}{\houtputs \cup O_H}{\store}
    $$
  \end{enumerate}
\end{definition}
